Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2024-02-01 RegReport/paper_nomarkup.tex
final version?

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we asked whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination}: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we asked 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. Based on pilot data, we predicted an association of pre-crastination with inefficient search strategies. Personality inventories were also administered to identify stable characteristics associated with these strategies. In the final dataset, there was no clear association between search strategy and pre-crastination, nor did these correlate strongly with any of the personality measures collected.}
\end{abstract}

@@

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{../pilot_experiment/scratch/acc.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{../pilot_experiment/scratch/rt.pdf}}
  \caption{The distribution of (a) accuracy and (b) reaction time measures in the split-half visual search task. Note that the $y$-axis for (b) has been $\log_2$-scaled. Dots represent points classed as outliers, defined as being below or above $1.5 \times$ the inter-quartile range away from the first or third quartile.}
  \label{fig:exp1_summary}
\end{figure}

@@

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_prior_plot.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_plot.pdf}}
  \caption{(a) Prior and (b) posterior distributions for the mean of the two groups of participants, and the difference between them. Our priors for the two groups are identical, hence the overlapping distributions.}
  \label{fig:exp1_strategy}
\end{figure}

@@

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/acc_main.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/rt_main.pdf}}
  \caption{The distribution of (a) accuracy and (b) reaction time measures in the split-half visual search task. Note that the $y$-axis for (b) has been $\log_2$-scaled. Dots represent points classed as outliers, defined as being below or above $1.5 \times$ the inter-quartile range away from the first or third quartile.}
  \label{fig:exp2_summary}
\end{figure}

@@

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/strat_hist.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pre_crastinate.pdf}}
  \caption{The distribution of (a) search strategy efficiency scores and (b) pre-crastination behaivours. We can see that there is a lot of variation in both measures. }
  \label{fig:exp2_strat_summary}
\end{figure}

@@

\begin{figure}[t]
  \centering  
\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/post_plot.pdf}}
\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pre_cras_consc.pdf}}
  \caption{(a) Posterior distributions for the mean of the two groups of participants, and the difference between them. (b) There is no evidence for a relationship between pre-crastination and conscientiousness}
  \label{fig:full_exp_strategy}
\end{figure}

@@

\begin{figure}[t]
  \centering  
\includegraphics[width=10cm]{../analysis/scratch/exp_strat.pdf}
  \caption{(\textit{left}) Relationship between the pre-crasination and each of the personality measures. The effect size measures the $95\%$ confidence interval for the mean difference between participants who precrastinated and those who didn't. (\textit{right}) Correlations between our search strategy metric and the personality measures. Effect size measures the $95\%$ confidence interval in Pearson's $r$.}
   \label{fig:exp_analysis}
\end{figure}

>>>>

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we asked whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination}: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we asked 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. Based on pilot data, we predicted an association of pre-crastination with inefficient search strategies. Personality inventories were also administered to identify stable characteristics associated with these strategies. In the final dataset, there was no clear association between search strategy and pre-crastination, nor did these correlate strongly with any of the personality measures collected.
\end{abstract}

@@

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{Figures/acc.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{Figures/rt.pdf}}
  \caption{The distribution of (a) accuracy and (b) reaction time measures in the split-half visual search task. Note that the $y$-axis for (b) has been $\log_2$-scaled. Dots represent points classed as outliers, defined as being below or above $1.5 \times$ the inter-quartile range away from the first or third quartile.}
  \label{fig:exp1_summary}
\end{figure}

@@

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{Figures/pilot_prior_plot.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{Figures/pilot_plot.pdf}}
  \caption{(a) Prior and (b) posterior distributions for the mean of the two groups of participants, and the difference between them. Our priors for the two groups are identical, hence the overlapping distributions.}
  \label{fig:exp1_strategy}
\end{figure}

@@

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{Figures/acc_main.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{Figures/rt_main.pdf}}
  \caption{The distribution of (a) accuracy and (b) reaction time measures in the split-half visual search task. Note that the $y$-axis for (b) has been $\log_2$-scaled. Dots represent points classed as outliers, defined as being below or above $1.5 \times$ the inter-quartile range away from the first or third quartile.}
  \label{fig:exp2_summary}
\end{figure}

@@

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{Figures/strat_hist.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{Figures/pre_crastinate.pdf}}
  \caption{The distribution of (a) search strategy efficiency scores and (b) pre-crastination behaivours. We can see that there is a lot of variation in both measures. }
  \label{fig:exp2_strat_summary}
\end{figure}

@@

\begin{figure}[t]
  \centering  
\subfigure[]{\includegraphics[width=6cm]{Figures/post_plot.pdf}}
\subfigure[]{\includegraphics[width=6cm]{Figures/pre_cras_consc.pdf}}
  \caption{(a) Posterior distributions for the mean of the two groups of participants, and the difference between them. (b) There is no evidence for a relationship between pre-crastination and conscientiousness}
  \label{fig:full_exp_strategy}
\end{figure}

@@

\begin{figure}[t]
  \centering  
\includegraphics[width=10cm]{Figures/exp_strat.pdf}
  \caption{(\textit{left}) Relationship between the pre-crasination and each of the personality measures. The effect size measures the $95\%$ confidence interval for the mean difference between participants who precrastinated and those who didn't. (\textit{right}) Correlations between our search strategy metric and the personality measures. Effect size measures the $95\%$ confidence interval in Pearson's $r$.}
   \label{fig:exp_analysis}
\end{figure}
